AiPoker - Implementation of a Poker Agent

### 2014-10-15 report/paper.tex
test cases working

\begin{equation} \label{eq:upperconfidence}
	v_{i} + C \cdot \sqrt{\frac{\ln N}{n_{i}}}
\end{equation}
The first term vi is the estimated value of the node and is responsible for exploitation of good nodes, the second term is made up by the total number of visits of the parent node $N$ and the total number of visits of the current node $n_{i}$. The constant $C$ allows tuning of the exploration-exploitation trade-off. 
\\*\\*
\textbf{Expansion}
\\*If the leaf node reached is not an terminating node, which means that the game is not over at the current node. Then create one or more child nodes from the node currently at. This step is illustrated in fig(\ref{fig:expansion}).
\begin{figure}[here]
  \begin{center}
    \includegraphics[scale=0.30]{img/tree1.png}
    \caption{\label{fig:expansion} Illustration of how the green node is added to the tree.}
  \end{center}
\end{figure}
\\*
\textbf{Simulation}
\\*The third step in MCTS is the simulation step. Here a game is simulated from the state in the new node until a result is achieved. The value of the reached result is recorded.
\\*\\*
\textbf{Backpropagation}
\\*The last step is to update the expected value and the selection counter for all nodes along the explored path by backpropagating the recorded result from the simulation step. This step is illustrated in fig(\ref{fig:backprop}).
\begin{figure}[here]
  \begin{center}
    \includegraphics[scale=0.30]{img/tree2.png}
    \caption{\label{fig:backprop} Illustration of how the path to the node is updated with the score from the simulation in the whole tree.}
  \end{center}
\end{figure}
When the backpropagation has been done the whole chain starts over again starting with the selection stage. [REF!] One of the pros with MCTS is that it is anytime, that is it will give a valid solution to the problem even if it is interrupted before it ends. However the quality of the solution is an estimate and is expected to be better the more time the MCTS keeps running.

>>>>

\begin{equation} \label{eq:upperconfidence}
	v_{i} + C \cdot \sqrt{\frac{\ln N}{n_{i}}}
\end{equation}
The first term vi is the estimated value of the node and is responsible for exploitation of good nodes, the second term is made up by the total number of visits of the parent node $N$ and the total number of visits of the current node $n_{i}$. The constant $C$ allows tuning of the exploration-exploitation trade-off. 
\\*\\*
\textbf{Expansion}
\\*If the leaf node reached is not an terminating node, which means that the game is not over at the current node. Then create one or more child nodes from the node currently at. This step is illustrated in fig(\ref{fig:expansion}).
\begin{figure}[here]
  \begin{center}
    \includegraphics[scale=0.30]{img/tree1.png}
    \caption{\label{fig:expansion} Illustration of how the green node is added to the tree.}
  \end{center}
\end{figure}
\\*
\textbf{Simulation}
\\*The third step in MCTS is the simulation step. Here a game is simulated from the state in the new node until a result is achieved. The value of the reached result is recorded.
\\*\\*
\textbf{Backpropagation}
\\*The last step is to update the expected value and the selection counter for all nodes along the explored path by backpropagating the recorded result from the simulation step. This step is illustrated in fig(\ref{fig:backprop}).
\begin{figure}[here]
  \begin{center}
    \includegraphics[scale=0.30]{img/tree2.png}
    \caption{\label{fig:backprop} Illustration of how the path to the node is updated with the score from the simulation in the whole tree.}
  \end{center}
\end{figure}
When the back propagation step is finished the whole chain starts over again starting with the selection step. This is done until the either the game tree is fully searched or a time limit is reached. The fact that MCTS can give a result after a given time is a result of it being anytime, that is it will give a valid solution to the problem even if it is interrupted before it is finished. However the quality of the solution is an estimate and is expected to be better the more time the MCTS keeps running.

One problem that is introduced with the MCTS is how to run the simulation step. Here we have to select the moves for each player until the end of the game. One solution could be to just select random moves, this can work well for simple games but for games as complex as poker this will lead to bad results. This implies that we somehow have to model the opponent to be able to determine the correct actions in the simulation.
